%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[doublespacing]{setspace}
\usepackage{cancel}
\usepackage{mdframed}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{tikz}
\usepackage{xcolor}
\usetikzlibrary{positioning,calc}
\title{On A Class of Uniform Algorithms}
\author{Sanat K. Basu}
\date{Jan 1, 1985}


\begin{document}
\newcommand\bigO[1]{$\mathcal{O}(#1)$}
\newcommand\cancelb{\cancel{b}}
\newcommand\cancelc{\cancel{c}}
\newcommand{\suchthat}{\ni}
\newenvironment{aside}
{\begin{mdframed}[leftline=false, rightline=false, leftmargin=2em, rightmargin=2em,
    innerleftmargin=0pt, innerrightmargin=0pt, linewidth=0.75pt,skipabove=7pt, skipbelow=7pt]\small}
{\end{mdframed}}

\newenvironment{error}
{\begin{mdframed}[backgroundcolor=red!10, leftline=false, rightline=false, leftmargin=2em, rightmargin=2em,
    innerleftmargin=0pt, innerrightmargin=0pt, linewidth=0.75pt,skipabove=7pt, skipbelow=7pt]\small}
{\end{mdframed}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

\maketitle
\begin{abstract}
A nondeterministic Turing machine model called S-machine is introduced.
This machine performs its computations during successive sweeps of the tape, using sets of states and sets of symbols.
A deterministic simulator of this machine in the form of a while-do loop is constructed.
A relation of equivalence between sets of states and a corresponding relation between sets of symbols is introduced.
These relations are then extended to define equivalence classes of crossing functions.
Information about the equivalence class of the crossing function of the scanned segment of the tape is contained
in a context graph.
A procedure for computing this graph is described.
It is shown that successive context graphs can be computed in a constant number of 
steps.
Using the context graph it is shown that the while-do simulator of the S-machine
is uniform over a linear data domain.
We then obtain a deterministic algorithm to
decide whether an input of size $n$ will be accepted by the S-machine.
This algorithm uses no more than \bigO{S(n)^2} steps where $S(n)$ is the spacebound
of the S-machine.
Corresponding results in terms of the standard Turing machine model are then derived.
\end{abstract}

\section{Introduction}\label{sec:introduction}
\input{introduction}

\section{A nondeterministic sweep machine (S-machine)}\label{sec:s_machine_definition}
\input{s_machine_definition}

\section{Equivalence of statesets and symbol sets}\label{sec:two}
\section{The left context graph}\label{sec:three}
\section{Properties of $G_i$}\label{sec:four}
\section{Uniformity of $\bar{P}_2$}\label{sec:five}
\section{Appendix}\label{sec:appendix}
\input{appendix}
\end{document}